Figures

### 2018-11-05 figures/05_cafos.Rmd
add cafos map

animals <- readRDS("../data/census/census.rds")
st_geometry(animals) <- NULL
animals <- left_join(ep, animals, by = "lagoslakeid")
animals <- dplyr::filter(animals, !(lagoslakeid %in% c(401, 6076)))

@@

theme_opts <- theme(legend.position = "none", 
                    axis.text = element_blank(), 
                    axis.ticks = element_blank(), 
                    title = element_text(size = 8), 
                    plot.margin = unit(c(0, -2, 0, -2), "cm"))

cowplot::plot_grid(
    ggplot() +
      geom_sf(data = states) +
      geom_sf(data = 
                dplyr::filter(animals, ), 
              aes(color = hog_sales), 
              size = 0.2, alpha = 0.8) +
      coord_sf(datum = NA) + 
      theme_minimal() + theme_opts +
      ggtitle("hog operations") +
      labs(color = paste0("hog \n operations")),
    ggplot() +
      geom_sf(data = states) +
      geom_sf(data = 
                dplyr::filter(animals, cattle_sales <= 6 & 
                                !is.na(cattle_sales)), 
              aes(color = cattle_sales), 
              size = 0.2, alpha = 0.8) +
      coord_sf(datum = NA) + 
      ggtitle("cattle operations") +
      theme_minimal() + theme_opts,
    ggplot() +
      geom_sf(data = states) +
      geom_sf(data = 
                dplyr::filter(animals, !is.na(cattle_dairy)), 
              aes(color = cattle_dairy), 
              size = 0.2, alpha = 0.8) +
      coord_sf(datum = NA) + 
      theme_minimal() + theme_opts +
      ggtitle("dairy operations") +
      labs(color = paste0("dairy \n operations")),
    ggplot() +
      geom_sf(data = states) +
      geom_sf(data = 
                dplyr::filter(animals, chicken_sales <= 30), 
              aes(color = chicken_sales), 
              size = 0.2, alpha = 0.8) +
      coord_sf(datum = NA) + 
      theme_minimal() + theme_opts +
      ggtitle("chicken operations") +
      labs(color = paste0("chicken \n operations")),
    ggplot() +
      geom_sf(data = states) +
      geom_sf(data = 
                dplyr::filter(animals, cattle_total <= 20000), 
              aes(color = cattle_total), 
              size = 0.2, alpha = 0.8, pch = 19) +
      coord_sf(datum = NA) + 
      theme_minimal() + theme_opts +
      ggtitle("cattle head") +
      labs(color = paste0("cattle \n head")), 
    ncol = 1)

>>>>

cafos_epa <- st_read("../data/cafos/CAFOs_per_County.shp")
cafos_epa <- cafos_epa[
  unlist(lapply(
    st_intersects(cafos_epa, states), function(x) length(x) > 0)),]

animals <- readRDS("../data/census/census.rds")
st_geometry(animals) <- NULL
animals <- left_join(ep, animals, by = "lagoslakeid")
# animals <- dplyr::filter(animals, !(lagoslakeid %in% c(401, 6076)))

@@

theme_opts <- theme(legend.position = "none", 
                    legend.title=element_blank(),
                    axis.text = element_blank(), 
                    axis.ticks = element_blank(), 
                    title = element_text(size = 8), 
                    plot.margin = unit(c(0, -2, 0, -2), "cm"))

log_breaks <- function(x, l_out){
  round(rev(exp(
    seq(
      log(min(x, na.rm = TRUE)), 
      log(max(x, na.rm = TRUE)), 
      length.out = l_out))), 1)
}

cowplot::plot_grid(

  ggplot() +
      geom_sf(data = states) +
      geom_sf(data = 
                dplyr::filter(animals, !is.na(hog_sales)), 
              aes(color = hog_sales), 
              size = 0.2, alpha = 0.8) +
      coord_sf(datum = NA) + 
      labs(color = paste0("hog \n operations")) +
      theme_minimal() + theme_opts +
      ggtitle("hog operations") +
      scale_color_gradient(breaks = log_breaks(animals$hog_sales, 8), 
                           trans = "log")
  ,
    ggplot() +
      geom_sf(data = states) +
      geom_sf(data = 
                dplyr::filter(animals, cattle_sales <= 6 & 
                                !is.na(cattle_sales)), 
              aes(color = cattle_sales), 
              size = 0.2, alpha = 0.8) +
      coord_sf(datum = NA) + 
      ggtitle("cattle operations") +
      labs(color = paste0("cattle \n operations")) +
      theme_minimal() + theme_opts +
      scale_color_gradient(breaks = log_breaks(animals$cattle_sales, 8), 
                           trans = "log"),
    ggplot() +
      geom_sf(data = states) +
      geom_sf(data = 
                dplyr::filter(animals, !is.na(cattle_dairy)), 
              aes(color = cattle_dairy), 
              size = 0.2, alpha = 0.8) +
      coord_sf(datum = NA) + 
      labs(color = paste0("dairy \n operations")) +
      theme_minimal() + theme_opts +
      ggtitle("dairy operations") +
      scale_color_gradient(breaks = log_breaks(animals$cattle_dairy, 8), 
                           trans = "log"),
    ggplot() +
      geom_sf(data = states) +
      geom_sf(data = 
                dplyr::filter(animals, chicken_sales <= 30), 
              aes(color = chicken_sales), 
              size = 0.2, alpha = 0.8) +
      coord_sf(datum = NA) + 
      labs(color = paste0("chicken \n operations")) +
      theme_minimal() + theme_opts +
      ggtitle("chicken operations") +
      scale_color_gradient(breaks = log_breaks(animals$chicken_sales, 8), 
                           trans = "log"),
    ggplot() +
      geom_sf(data = states) +
      geom_sf(data = 
                dplyr::filter(animals, cattle_total <= 20000), 
              aes(color = cattle_total), 
              size = 0.2, alpha = 0.8, pch = 19) +
      coord_sf(datum = NA) + 
      labs(color = paste0("cattle \n head")) +
      theme_minimal() + theme_opts +
      ggtitle("cattle head") +
      scale_color_gradient(breaks = log_breaks(animals$cattle_total, 8), 
                           trans = "log"), 
  ggplot() +
      geom_sf(data = cafos_epa, aes(fill = CAFOs), color = "transparent") +
      geom_sf(data = states, fill = "transparent") +
      coord_sf(datum = NA) + 
      theme_minimal() + theme_opts +
      ggtitle("CAFOS"),
    ncol = 1)
